\documentclass[addpoints]{exam}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\newcommand{\RN}[1]{%
  \textup{\uppercase\expandafter{\romannumeral#1}}%
}
\input{header.tex}

\title{Lab 11 Quiz}
\date{Week 11}
\begin{document} 

\Instructions

\begin{enumerate}
\vspace{2em}



\newline

\item
\question \pts{3} \tf If an object and all its connected components implement \textsc{Serializable}, then you can read \& write via File I/O.

\newline
\Ans True
\newline
\item
\question \pts{4}


Consider the following main method for Q4:

\begin{lstlisting}
public static void main(String[] args) {
    for(int i = 0; i < args.length; i++) {
        File f;
        BufferedReader r;
        try {
            f = new File(args[i]);
            r = new BufferedReader(new FileReader(f));
        }
        catch(FileNotFoundException e) {
		    e.printStackTrace();
            continue;
        }
        finally {
            System.out.println("Working on file " + args[i]);
        }
    }
}
\end{lstlisting}

Circle the correct statements:
\newline

\RN{1}. As soon as a FileNotFoundException is thrown, the catch statement will print a stacktrace and immediately continue executing the for loop.

\RN{2}. As soon as a FileNotFoundException is thrown, the catch statement will print a stacktrace and the program will exit.

\RN{3}. As soon as a FileNotFoundException is thrown, the program will print a stacktrace, execute the finally clause, then continue executing the for loop. \Ans

\RN{4}. When there is no exception, the finally clause will still be executed. \Ans

\RN{5}. The finally clause is only executed when an exception is thrown.



\item
\question \pts{3} How should catch statements be ordered when dealing with multiple exceptions? 
\newline
\begin{choices} 

 \choice Order doesn't matter 
 
 \choice \Ans Exceptions should be ordered from specific to generalized. 
 
 \choice Exceptions should be ordered from generalized to specific. 
 

\end{choices}

\newline
\newline

\vspace{2em}
\end{enumerate}
\end{document}
              