\documentclass[addpoints]{exam}
\usepackage[utf8]{inputenc}
\input{header.tex}

\title{Lab 14 Quiz}
\date{Week 14}
\begin{document} 

\Instructions
\begin{enumerate}
\newline
\item \pts{2}
Which of these is \textbf{not} a dynamic data structure?

\begin{oneparchoices} 
\hspace{0.2cm}
 
 \choice Queue \newline
 
 \choice \Ans Array \newline
 
 \choice LinkedList\newline
 
 \choice Stack \newline
 \end{oneparchoices}
 
\item \pts{2} Complete the expressions for String a and String b, where ``a" stores the element at index 0 of List one, and ``b" stores the element at index 0 of List two.
\newline
\begin{lstlisting}
   List one = new ArrayList();
	one.add("Hello");
	
	List<String> two = new ArrayList<String>();
	two.add("World");

	String a =                          // TODO 1
	String b =                          // TODO 2

\end{lstlisting}
\Ans Without the use of generics, a cast is needed for ArrayList one.

\item \pts{2}
Which of these is \textbf{not} true about a Stack?

\begin{oneparchoices} 
\hspace{0.2cm}
 
 \choice  A Stack could be implemented with a LinkedList. \newline
 
 \choice \Ans Stacks are first-in, first-out. \newline
 
 \choice New items can be added at the top of the Stack \newline
 
 \choice A Stack can store any object type. \newline
 \end{oneparchoices}

\item \pts{4}
Think about the DynamicBuffer class that you implemented in Project 4. Consider these functionalities for the DynamicBuffer;
\begin{lstlisting}
   void addEmail ( Email email ); 		// Add an email 
	boolean remove( int i ); 			    // Remove ith email
	Email[] getNewest( int n ); 		    // Get n most recent emails.    
\end{lstlisting}
From the dynamic data structures Queue, LinkedList, and HashMap which \textbf{one} would best fulfill these functionalities and why?
\newline
\newline
\Ans Implementing a LinkedList would would meet the required functionalities as it maintains both an order to the emails (satisfying removing the ith email), as well as getting the n newest.
\newline

\vspace{2em}
\end{enumerate}
\end{document}
              